### 2019-10-18 ch6_bred/content.tex
~

One of the central cellular processes underlying development is transcriptional regulation. During development, changes in transcription factor activity induce chromatin modifications, chromatin remodelling and ultimately a differential recruitment of the basal transcriptional machinery \cite{coulon_eukaryotictranscriptionaldynamics_2013}. Modelling the dynamics of gene regulation is therefore essential to better understand why a cellular dynamic processes progresses through several steps, and what goes wrong in the case of disease.

>>>>

One of the central cellular processes underlying development is transcriptional regulation. 
Changes in transcription factor activity induce chromatin modifications, 
chromatin remodelling, a differential recruitment of the basal transcriptional machinery\cite{coulon_eukaryotictranscriptionaldynamics_2013}.
Modelling the dynamics of gene regulation is therefore essential to better understand
why a cellular dynamic processes progresses through several steps,
and what goes wrong in the case of disease.

### 2019-10-18 chX_backmatter.tex
~

\section{Co-author publications}
\begin{itemize}
	\item Decock A, Ongenaert M, \textbf{Cannoodt R}, Verniers K, De Wilde B, Laureys G, Van Roy N, Berbegall AP, Bienertova-Vasku J, Bown N, Clément N. Methyl-CpG-binding domain sequencing reveals a prognostic methylation signature in neuroblastoma. Oncotarget. 2016 Jan 12;7(2):1960.
	\item Van Cauwenbergh C, Van Schil K, \textbf{Cannoodt R}, Bauwens M, Van Laethem T, De Jaegere S, Steyaert W, Sante T, Menten B, Leroy BP, Coppieters F. arrEYE: a customized platform for high-resolution copy number analysis of coding and noncoding regions of known and candidate retinal dystrophy genes and retinal noncoding RNAs. Genetics in Medicine. 2017 Apr;19(4):457.
	\item Claeys S, Denecker G, \textbf{Cannoodt R}, Kumps C, Durinck K, Speleman F, De Preter K. Early and late effects of pharmacological ALK inhibition on the neuroblastoma transcriptome. Oncotarget. 2017 Dec 5;8(63):106820.
	\item Depuydt P, Boeva V, Hocking TD, \textbf{Cannoodt R}, Ambros IM, Ambros PF, Asgharzadeh S, Attiyeh EF, Combaret V, Defferrari R, Fischer M. Genomic amplifications and distal 6q loss: novel markers for poor survival in high-risk neuroblastoma patients. JNCI: Journal of the National Cancer Institute. 2018 Mar 5;110(10):1084-93.
	\item Scott CL, T'Jonck W, \ldots, \textbf{Cannoodt R}, Saelens W \ldots, Guilliams M. The transcription factor ZEB2 is required to maintain the tissue-specific identities of macrophages. Immunity. 2018 Aug 21;49(2):312-25.
	\item Saelens W, \textbf{Cannoodt R}, Saeys Y. A comprehensive evaluation of module detection methods for gene expression data. Nature communications. 2018 Mar 15;9(1):1090.
	\item Todorov H, \textbf{Cannoodt R}, Saelens W, Saeys Y. Network Inference from Single-Cell Transcriptomic Data. In Gene Regulatory Networks 2019 (pp. 235-249). Humana Press, New York, NY..
	\item Van den Berge K, De Bezieux HR, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S, Clement L. Trajectory-based differential expression analysis for single-cell sequencing data. BioRxiv. 2019 Jan 1:623397.
	\item Weber LM, Saelens W, \textbf{Cannoodt R}, Soneson C, Hapfelmeier A, Gardner PP, Boulesteix AL, Saeys Y, Robinson MD. Essential guidelines for computational method benchmarking. Genome biology. 2019 Dec;20(1):125.
	\item Lorenzi L, \ldots, \textbf{Cannoodt R}, \ldots, Mestdagh P. The RNA-Atlas, a single nucleotide resolution map of the human transcriptome. In preparation.
	\item Van den Berge K, Roux de Bézieux H, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S. Trajectory-based differential expression analysis. Submitted to Nature Communications.
	\item Van de Sande B, \ldots, \textbf{Cannoodt R}, \ldots, Saeys Y, Aerts S. A scalable SCENIC workflow for single-cell gene regulatory network analysis. Submitted to Nature Protocols.
\end{itemize}

@@

Packages that were created as part of this work are hosted on Github under the username rcannood\footnote{\url{https://github.com/rcannood?tab=repositories}} or the dynverse organisation\footnote{\url{https://github.com/dynverse?tab=repositories}}. As part of our standard development practices, we automate execution of unit tests and write extensive documentation to ensure the code complies with CRAN policy before submission. We aim to submit all other packages to CRAN as well.

We also helped maintain or extend other packages on Github, CRAN or Bioconductor on which our software depends. This includes speeding up parts of the dependency (slingshot), adding new functionality (devtools, ParamHelpers), fixing bugs (proxyC, rlang, monocle, splatter, slingshot), becoming a maintainer of orphaned packages (diffusionMap, princurve, GillespieSSA), and extending the documentation (devtools, mlr, remotes). Several of these package receive millions of downloads per year (devtools, remotes, rlang).

>>>>

\section{Co-author publications}
\begin{itemize}
	\item Decock A, Ongenaert M, \textbf{Cannoodt R}, Verniers K, De Wilde B, Laureys G, Van Roy N, Berbegall AP, Bienertova-Vasku J, Bown N, Clément N. Methyl-CpG-binding domain sequencing reveals a prognostic methylation signature in neuroblastoma. Oncotarget. 2016 Jan 12;7(2):1960.
	\item Van Cauwenbergh C, Van Schil K, \textbf{Cannoodt R}, Bauwens M, Van Laethem T, De Jaegere S, Steyaert W, Sante T, Menten B, Leroy BP, Coppieters F. arrEYE: a customized platform for high-resolution copy number analysis of coding and noncoding regions of known and candidate retinal dystrophy genes and retinal noncoding RNAs. Genetics in Medicine. 2017 Apr;19(4):457.
	\item Claeys S, Denecker G, \textbf{Cannoodt R}, Kumps C, Durinck K, Speleman F, De Preter K. Early and late effects of pharmacological ALK inhibition on the neuroblastoma transcriptome. Oncotarget. 2017 Dec 5;8(63):106820.
	\item Depuydt P, Boeva V, Hocking TD, \textbf{Cannoodt R}, Ambros IM, Ambros PF, Asgharzadeh S, Attiyeh EF, Combaret V, Defferrari R, Fischer M. Genomic amplifications and distal 6q loss: novel markers for poor survival in high-risk neuroblastoma patients. JNCI: Journal of the National Cancer Institute. 2018 Mar 5;110(10):1084-93.
	\item Scott CL*, T'Jonck W*, Martens L, Todorov H, Sichien D, Soen B, Bonnardel J, De Prijck S, Vandamme N, \textbf{Cannoodt R}, Saelens W, Vanneste B, Toussaint W, De Bleser P, Takahashi N, Vandenabeele P, Henri S, Pridans C, Hume DA, Lambrecht BN, De Baetselier P, Milling SWF, Van Ginderachter JA, Malissen B, Berx G, Beschin A, Saeys Y, Guilliams M. The transcription factor ZEB2 is required to maintain the tissue-specific identities of macrophages. Immunity. 2018 Aug 21;49(2):312-25.
	\item Saelens W, \textbf{Cannoodt R}, Saeys Y. A comprehensive evaluation of module detection methods for gene expression data. Nature communications. 2018 Mar 15;9(1):1090.
	\item Todorov H, \textbf{Cannoodt R}, Saelens W, Saeys Y. Network Inference from Single-Cell Transcriptomic Data. In Gene Regulatory Networks 2019 (pp. 235-249). Humana Press, New York, NY.
	\item Van den Berge K, De Bezieux HR, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S, Clement L. Trajectory-based differential expression analysis for single-cell sequencing data. bioRxiv. 2019 Jan 1:623397.
	\item Weber LM, Saelens W, \textbf{Cannoodt R}, Soneson C, Hapfelmeier A, Gardner PP, Boulesteix AL, Saeys Y, Robinson MD. Essential guidelines for computational method benchmarking. Genome biology. 2019 Jun;20(1):125.
	\item Lorenzi L*, Hua-Sheng C*, Avila Cobos F, Gross S, Volders PJ, \textbf{Cannoodt R}, Nuytens J, Vanderheyden K, Anckaert J, Lefever S, Goovaerts T, Hansen TB, Kuersten S, Nijs N, Taghon T, Vermaelen K, Brache KR, Saeys Y, De Meyer T, Deshpande N, Anande G, Chen TW, Wilkins MR, Unnikrishnan A, De Preter K, Kjerns J, Koster J, Schroth GP, Vandesompele J, Surnazin P, Mestdagh P. The RNA Atlas, a single nucleotide resolution map of the human transcriptome. bioRxiv. 2019 Oct:807529. Submitted to Nature. 
	\item Van den Berge K, Roux de Bézieux H, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S. Trajectory-based differential expression analysis. Submitted to Nature Communications.
	\item Van de Sande B, Flerin C, Davie K, De Waegeneer M, Hulselmans G, Aibar S, Seurinck R, Saelens W, \textbf{Cannoodt R}, Rouchon Q, Verbeiren T, De Maeyer D, Reumers J, Saeys Y, Aerts S. A scalable SCENIC workflow for single-cell gene regulatory network analysis. Submitted to Nature Protocols.
\end{itemize}

@@

Packages that were created as part of this work are hosted on Github under the username rcannood\footnote{\url{https://github.com/rcannood?tab=repositories}} or the dynverse organisation\footnote{\url{https://github.com/dynverse?tab=repositories}}. As part of our standard development practices, we automate execution of unit tests and write extensive documentation to ensure the code complies with CRAN policy before submission. Many of the packages are already hosted on CRAN, or are in the process of being prepared for submission.

We also helped maintain or extend other packages on Github, CRAN or Bioconductor on which our software depends. This includes speeding up parts of the dependency (slingshot), implementing new functionality (devtools, ParamHelpers, ranger, rlang), fixing bugs (proxyC, rlang, monocle, splatter, slingshot), becoming a maintainer of orphaned packages (diffusionMap, princurve, GillespieSSA), and extending the documentation (devtools, mlr, remotes). Several of these packages are mainstream R packages which receive millions of downloads per year (devtools, ranger, remotes, rlang).
